\chapter{Introduction}
\label{ch1}

\textcolor{blue}{autonomous robots}

%Autonomous robots are expected to perceive their environment, make decisions independently, and operate without continuous human control.
%Autonomous robots are expected to perceive their environment, independently make decisions and adapt to a changing environment without requiring human intervention.
Autonomous robots are expected to perceive their environment, make decisions independently, and adapt to changes without requiring human intervention.
%In such systems, humans primarily take a supervisory role, intervening only when necessary to adjust high-level objectives or ensure safety.
%Human operators only take a supervisory role, having the option to intervene when desire.
Human operators typically take a supervisory role, with the option to intervene when desired.

\textcolor{blue}{swarm robotics}

Swarm robotics is a decentralized robotic paradigm inspired by collective behaviors observed in natural systems such as insect colonies and animal groups
    \cite{bonabeau1999swarm}.
In these systems, complex global behaviors emerge from simple local interactions, without relying on centralized control or global information.
%By following the same principle, swarm robotic systems naturally exhibit desirable properties including scalability, fault tolerance, and adaptability
By following the same principle, robot swarms naturally exhibit desirable properties including scalability, fault tolerance, and adaptability
    \cite{dorigo2014swarm,
          dorigo2020reflections,
          dorigo2021swarm}.
%As the swarm size increases, performance can be maintained without centralized bottlenecks, while the failure of individual robots does not critically affect the overall system behavior.
The absence of centralized control avoids communication and computation bottlenecks, allowing the system to scale to large populations.
Redundancy in the number of robots provides inherent fault tolerance, such that the failure of individual agents does not critically affect overall system behavior.
%These characteristics make swarm robotics particularly attractive for large-scale, distributed, and dynamic real-world applications, such as
%    environmental monitoring
%    \cite{talamali2021less},
%    navigation and transportation
%    \cite{dorigo2013swarmanoid},
%    self-assembly
%    \cite{rubenstein2014programmable},
%    and collective construction
%    \cite{team2012designing, petersen2019review}.
These characteristics make robot swarms particularly attractive for pplications that require large numbers of robots.

\textcolor{blue}{However}

%However, swarm robotic systems typically rely on local sensing and local communication, with each robot having access to only partial information about the global state.
However, robot swarms typically rely on local sensing and local communication, with each robot having access to only partial information about the global state.
As a result, reaching consistent swarm-level decisions can be slow or inefficient.
The lack of centralized control mechanism also complicates human swarm interaction.
These limitations restrict the level of autonomy and manageability that swarm systems can achieve in complex and dynamic tasks.

%%%%%%%%%
% - self-organizing hierarchy is interesting (cite Marco SR perspective), explain why
% - because it is interesting, I have been involved in the development of a research line to apply self-organizing hierarchy to robot swarms
% - this research line has been inspired by work to apply self-organizing hierarchy to physically-connected robots -- explain and introduce MNS
% - the research line has explored how to extend the MNS starting point to robot swarms more generally and to assess the added value of using self-organizing hierarchy in robot swarms
% - these studies (cite all the ones where you are not the first author and/or not a co-author) contributed results in simulation and theoretical analysis that demonstrate the feasibility and usefulness of applying self-organizing hierarchy to robot swarms
% - this thesis contributes the first formalization of the full concept (check our SR for wording) and the first proof-of-concept with real robots -- called the SoNS
% - after introducing the SoNS, this thesis also extends the SoNS in XX and XX way
% - (make sure that you communicate to the reader why your 3 research chapters make an important contribution to the field)

\textcolor{blue}{Self-organizing hierarchy in swarm robotics}

Self-organizing hierarchical organization provides a promising approach to addressing the paradox between centralized and decentralized multi-robot systems.
    \cite{dorigo2020reflections}.  % Marco reflections
A hierarchical structure provides directed information flow as a form of global coordination.
At the same time, the structure is constructed in a self-organized manner, preserving the scalability and fault tolerance of the system.
Such organization can improve collective decision making and facilitate coordinated behavior at the swarm level, without introducing centralized bottlenecks.

\textcolor{blue}{research line}

Motivated by these potential benefits, this research line has been investigating how self-organizing hierarchical structures can be applied to robot swarms.
It originates from the concept of the Mergeable Nervous System (MNS)
    \cite{mathews2017mergeable},
which demonstrated how a decentralized group of physically connected robots can self-organize into a temporary centralized control structure.
Building on the MNS concept, subsequent studies explored the application of self-organizing hierarchy to tasks such as formation control and coverage, and analyzed the resulting trade-offs between performance, scalability, and robustness
    \cite{jamshidpey2020multi,
          jamshidpey2023reducing,
          jamshidpey2024centralization,
          zhang2023self,
          ouguz2025proactive}.
Through simulation studies and theoretical analysis, this body of work demonstrated the feasibility and usefulness of introducing self-organizing hierarchical organization into robot swarms.

\textcolor{blue}{This thesis}

This thesis proposes a complete framework termed the Self-organizing Nervous Swarm (SoNS),
which extends the concept of self-organizing hierarchy from physically connected robots to general robot swarms
    \cite{zhu2020formation,
          zhu2024self}.
The SoNS formalizes how hierarchical structures can emerge, be maintained, and be reconfigured using only local sensing and communication, without relying on centralized control or global information.

The framework specifies a set of local interaction rules that govern the coordination among heterogeneous robots while preserving the principles of swarm intelligence.
Through continuous local coordination, the swarm spontaneously forms a hierarchical communication topology that enables guided information flow across the swarm.
Leveraging this emergent structure, efficient task assignment and formation control can be achieved without requiring global knowledge.

Furthermore, this thesis also demonstrates that the SoNS framework simplifies the design of autonomous behaviors of the robot swarms.
In particular, robots can transfer control code among themselves and dynamically reprogram their behaviors to adapt to changing tasks and environments.
Finally, the thesis shows that SoNS facilitates scalable human--swarm interaction, allowing a human operator to steer and reprogram the entire swarm by communicating with a single robot.

\iffalse
\textcolor{blue}{hierarchy}

%Hierarchical organization provides a promising approach to addressing the paradox between centralized and decentralized multi-robot systems.
Self-organizing hierarchical organization provides a promising approach to addressing the paradox between centralized and decentralized multi-robot systems.
%By introducing structured information flow, hierarchical approaches enable limited forms of global coordination while preserving local interactions among robots.
On one hand, a hierarchical structure provides directed information flow to introduce a form of global coordination.
In the meantime, the structure is constructed in a self-organized way to keep scalability and fault tolerance.
Such organization can improve collective decision making, support scalable human supervision, and facilitate coordinated behavior at the swarm level.
Importantly, when designed appropriately, hierarchical methods can retain the scalability and robustness that characterize swarm robotics.
robot swarms

\textcolor{blue}{SoNS research line old}

Existing work has already proved that hierarchical structures can be used to improve swarm robotics.
MNS tries to form a centralized control structure in a decentralized way.
    \cite{mathews2017mergeable}
Later work extend this idea to formation and coverage.
    \cite{zhang2023self}
    \cite{jamshidpey2020multi}
    \cite{jamshidpey2024centralization}
    \cite{jamshidpey2023reducing}
    \cite{ouguz2025proactive}
    \textcolor{red}{my paper ?}
    \cite{zhu2020formation}
    \cite{zhu2024self}

\textcolor{blue}{This thesis}

This thesis proposes a self-organizing hierarchical framework for swarm robotics.
The objective is to unify autonomous decision making, scalable coordination, and human–swarm interaction under strict local-information constraints.
The proposed framework demonstrates how hierarchical structures can emerge and be maintained without centralized control.
Through this approach, the thesis shows how hierarchy can be leveraged as an enabling mechanism rather than a violation of swarm principles.



\textcolor{blue}{SoNS research line new}

A series of studies conducted within our research group has systematically investigated how hierarchical control structures can be formed and exploited in robot swarms through purely local interactions.
This line of research aims to reconcile the scalability and robustness of decentralized swarms with the coordination efficiency typically associated with centralized control.

The concept was first introduced through the Mergeable Nervous System (MNS), which demonstrated that a group of physically connected robots can form a centralized control structure
    \cite{mathews2017mergeable}.
Building upon this foundation, our subsequent work extended the approach to concrete swarm tasks, including formation control and area coverage, showing that self-organizing hierarchies can significantly improve coordination efficiency while preserving scalability
    \cite{zhang2023self,
          jamshidpey2020multi,
          jamshidpey2024centralization,
          jamshidpey2023reducing,
          oguz2025proactive,
          zhu2020formation,
          zhu2024self}.
Together, these works establish the Self-organizign Nervous System, which is self-organizing hierarchy as a viable and effective mechanism for structured coordination in robot swarms.

This thesis proposes a novel framework named Self-organizing Nervous Swarm (SoNS), which aims to bring the benefits of centralized coordination into a fully decentralized, self-organizing swarm system.
In SoNS, each robot follows strictly local interaction rules based on nearby sensing and communication, maintaining the principles of swarm intelligence.
In the meantime, through continuous coordination with neighboring agents, the swarm spontaneously forms a hierarchical communication topology, allowing information to flow across the topology of the hierarchy in a guided way.
Harnessing this emergent structure, efficient task assignment can be demonstrated for formation control can be achieved without requiring global knowledge.
Furthermore, the SoNS framework is shown to simplify the design of autonomous behaviors, allowing robots to transfer codes to each other and re-program themselves to adapt to dynamic tasks and environments.
Lastly, this thesis shows that SoNS facilitates scalable human–swarm interaction, where a human operator steer and reprogram the whole swarm by communicating with only one robot.


\textcolor{blue}{One version}

The SoNS defines how hierarchical structures can emerge, be maintained, and be reconfigured using only local sensing and communication, without relying on centralized control or global information.
Beyond formalization, this thesis presents the first proof-of-concept implementation of such a framework on real robot swarms, demonstrating its practicality under real-world constraints

This Thesis proposes a complete framework named Self-organizing Nervous Swarm (SoNS), which aims to go beyond physical connected ground robots.
    \cite{zhu2020formation,
          zhu2024self}.
This Thesis describe the full set of local remote interaction rules between different types of robots based on nearby sensing and communication, maintaining the principles of swarm intelligence.
In the meantime, through continuous coordination with neighboring agents, the swarm spontaneously forms a hierarchical communication topology, allowing information to flow across the topology of the hierarchy in a guided way.
Harnessing this emergent structure, efficient task assignment can be demonstrated for formation control can be achieved without requiring global knowledge.
Furthermore, the SoNS framework is shown to simplify the design of autonomous behaviors, allowing robots to transfer codes to each other and re-program themselves to adapt to dynamic tasks and environments.
Lastly, this thesis shows that SoNS facilitates scalable human–swarm interaction, where a human operator steer and reprogram the whole swarm by communicating with only one robot.

\fi